---
name: Dennis
surname: Sobolewski
position: "Data Scientist"
address: "Chicago, Illinois"
phone: +1 609 280 4734
www: dsobolew.me
email: "Dennis.Sobolewski@gmail.com"
twitter: djsobolew
github: dsobolew
linkedin: dsobolew
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 414141
output: vitae::awesomecv
---


<style type="text/css">
  body{
  font-size: 9pt;
}
,
h1{
  font-size: 10pt;
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, dpi = 180)
library(vitae)
```

# Data Scientist with 5+ Years of Healthcare Experience

* Experience providing solutions for clients ranging from community hospitals to academic medical centers.
* Skilled at extracting and tidying multi-source data, applying advanced data science techniques and validating output, and effectively visualizing results.
* Capable of translating complex statistical analyses in easy-to-understand terms.

\vspace{-1truemm}

# Education
```{r education}
tibble::tribble(
  ~ degree, ~ uni, ~ loc, ~ dates,
  "MSc in Business Analytics", "University of Notre Dame", "South Bend, Indiana", "2015 - 2016",
  "Bachelor of Finance", "University of Notre Dame", "South Bend, Indiana", "2007 - 2011", 
) %>% 
  detailed_entries(degree, dates, uni, loc)
```

\vspace{-5truemm}

# Work Experience

```{r consulting}

tibble::tribble(
  ~ role, ~ company, ~ loc, ~ dates, ~ details,
  "Data scientist", "Bluetree Network", "Madison, WI", "Mar. 2018 - Present", "Built forecasting models to predict patient access center call volumes and applied queueing theory principals to determing optimal staffing levels.",
    "Data scientist", "Bluetree Network", "Madison, WI", "Mar. 2018 - Present", "Designed and co-developed a custom patient access center data warehouse using MS Visual Studio for automatic deployment and ingestion of multiple data sources.",
    "Data scientist", "Bluetree Network", "Madison, WI", "Mar. 2018 - Present", "Performed spatial autocorrelation tests on ICD codes within a patient population to determine areas of statistically significant clustering and dispersion.",
    "Data scientist", "Bluetree Network", "Madison, WI", "Mar. 2018 - Present", "Developed a Case Mix Index predictive model to identify under and over-coded hospital accounts to maximise reimbursement and reduce denials.",
    "Data scientist", "Bluetree Network", "Madison, WI", "Mar. 2018 - Present", "Perform exploratory data analyses on multiple Epic healthcare data sources and communicated results for project decision-making.",
      "Data scientist", "Bluetree Network", "Madison, WI", "Mar. 2018 - Present", "Developed custom clarity and caboodle queries, validated the output, and build operational tableau dashboards for both executives and ground team members within healthcare organizations.",
    "Analytics Specialist", "Northern Trust Corporation", "Chicago, IL", "Jul. 2014 - Mar. 2018", "Developed a data validation tool that performed regression testing of data models between staging and production environments and provided readable results.",
  "Analytics Specialist", "Northern Trust Corporation", "Chicago, IL", "Jul. 2014 - Mar. 2018", "Built and managed an automated processes tp audit security permissions within Nothern Trust's proprietary hedge fund administration software.",
  "Quality Assurance Analyst", "Epic", "Madison, WI", "Jul. 2011 - Jul. 2014", "Designed and tested Epic's proprietary healthcare software alongside developers and implementation staff.",
    "Quality Assurance Analyst", "Epic", "Madison, WI", "Jul. 2011 - Jul. 2014", "Trained clients on using new functionalities within the HB, PB, and Claims and Remittance Epic modules."
) %>% 
  detailed_entries(role, dates, company, loc, details)


```

\vspace{-3truemm}

# Skills and Technologies
```{r fig.height=1.8, fig.width=2.5, fig.align='center'}

# Library
library(fmsb)
 
# Create data: note in High school for Jonathan:
data <- as.data.frame(matrix( c(20, 18, 15, 15, 18, 20, 12, 10, 5) , ncol=9))
colnames(data) <- c("R-coding" , "Tableau" , "Git"  , "Machine\n Learning" ,"SQL" , "Data-Viz" ,"DevOps","Visual\n Studio" , "Python")
 
# To use the fmsb package, I have to add 2 lines to the dataframe: the max and min of each topic to show on the plot!
data <- rbind(rep(20,10) , rep(0,10) , data)
 
# Check your data, it has to look like this!
# head(data)

par(oma=c(0,0,0,0),mar=c(0,0,0,0)+.2)

# Custom the radarChart !
radarchart( data  , axistype=1 , 
 
    #custom polygon
    pcol=rgb(0.2,0.5,0.5,0.9) , pfcol=rgb(0.2,0.5,0.5,0.5) , plwd=4 , 
 
    #custom the grid
    cglcol="grey", cglty=1, axislabcol="grey", caxislabels=seq(0,20,5), cglwd=0.8,
 
    #custom labels
    vlcex=0.8 
    )

#box(col="red")

#box("figure", col="forestgreen")  
 
#box("outer", col="blue")  

```
